### 2010-01-27 thesis/SensorMLOnSenseTile/trunk/thesis/SensorMLonSenseTileThesis.tex
minor updates
static diagram for data provider added

@@

\chapter{SensorML}
\section{SensorML Overview}
The Open Geospatial Consortium (OGC) Sensor Web Enablement (SWE) [ref]  is establishing interfaces and protocols that will enable a standerised “Sensor Web”. It is hoped that an easier integration and development of sensor applications across sensor networks will be facilitated by this standarising activity. Sensor Modelling Language (SensorML) is one part of the SWE initiative and is used to describe sensor systems and the processing of observations from sensor systems.

@@

@@

 \begin{figure}
\includegraphics{SensorML_SenseTile_System_design_tuple_pa3.png}
\caption{Block diagram of SenseTile System process}\label{fig:SensorML_SenseTile_design.png}
\end{figure}

@@

\section{SenseTile Web Service}
\subsection{Overview}
 \begin{figure}
\scalebox{0.65}{\includegraphics{SystemOverview.png}}
\caption{SenseTile System Overview}\label{fig:SystemOverview.png}
\end{figure}

@@

\subsection {DataProvider}

Keeps track of sensorboards that register

>>>>

This description is executed on the processing unit as part of a webservice to generate data.
SOS. Implemation added to allow the description to be used to generate observations. Processing of data.

@@

\chapter{SensorML}
\section{SensorML Overview}
The Open Geospatial Consortium (OGC) Sensor Web Enablement (SWE) [ref]  is establishing interfaces and protocols that will enable a standardised “Sensor Web”. It is hoped that an easier integration and development of sensor applications across sensor networks will be facilitated by this standarising activity. Sensor Modelling Language (SensorML) is one part of the SWE initiative and is used to describe sensor systems and the processing of observations from sensor systems.

@@

including measurement by a sensor system, as well as post-measurement
processing.

@@

 \begin{figure}
\scalebox{0.65}{\includegraphics{SenseTileSystem.pdf}}
\caption{SenseTile System Overview}\label{fig:SenseTileSystem.pdf}
\end{figure}

 \begin{figure}
\scalebox{0.65}{\includegraphics{SensorML_SenseTile_System_2_pa1.pdf}}
\caption{SenseTile System Components}\label{fig:SensorML_SenseTile_System_2_pa1.pdf}
\end{figure}

@@

\section{SenseTile Web Service}
\subsection{Overview}

Web Service - SOS -standard access to sensor observations

SOS diagram

DataProvider

DataProducer

Deployment Scenarios - diagram

Flexible Division - several dataproducers can register with one DataProvider.

Seperate processes rmi.
 \begin{figure}
\scalebox{0.65}{\includegraphics{SystemOverview.png}}
\caption{Overview}\label{fig:SystemOverview.png}
\end{figure}

@@

\subsection {DataProvider}
 \begin{figure}
\scalebox{0.65}{\includegraphics{bon_static_diagam_provider.png}}
\caption{DataProvider Static Diagram}\label{fig:bon_static_diagam_provider.png}
\end{figure}
Keeps track of sensorboards that register
